analysis-pilot

### 2023-07-25 code/analysis-pilot.Rmd
accuracy 14:19

#rename columns
```{r}
colnames(filtered_data)[1] = "Date" %>% 
colnames(filtered_data)[]

>>>>

#accuracy
```{r}
accuracy <- filtered_data %>% 
  group_by(gameId) %>% 
  summarize(total=n(),
            correct=sum(countCorrect)) %>% 
  mutate(fraction = correct/total*100)

View(accuracy)
```

#graph accuracy to time
#graph accuracy

#rename columns
```{r}
colnames(filtered_data)[1] = "Date" %>% 
#colnames(filtered_data)[]
